---
title: "AL Report"
description: |
  Examination of AL data from 21-22
author:
  - name: Kasey Dye
    affiliation:  Office of Research & Evaluation
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 2
---

# Executive Summary

TODO LATER

# Background

ADD SOME BACKGROUND HERE. A PARAGRAPH OR SO.

# To Include

- Teacher Usage. By School and by Content. And by District
- Group usage by types: using existing assignments; personalizing; not using at all
- Variance within schools/content
- Usage by school level -- MS/HS
- Potentially bring in SOL data, although some concerns about this
- Identify gaps in available data that would be useful to ask for

# Teacher Usage

## Division-Level

```{r setup, include = FALSE, echo = FALSE}
library(tidyverse)

df_raw <- read_csv(here::here("data/small_df_anon.csv"))

# combine co-taught stuff
df <- df_raw |>
    mutate(
        total_ss = number_active_students + number_active_students_for_co_taught_classes,
        total_assign = number_of_assignments + number_of_assignments_for_co_taught_classes,
        total_s_time = total_active_learning_time + total_active_learning_time_for_co_taught_classes
    ) |>
    # standardize time per student
    mutate(
        time_per_s = total_s_time / total_ss
    )
# may want to clean this up a little more
```

some exploratory plots:

total time per student for all teachers

```{r}
ggplot(df, aes(time_per_s)) +
    geom_histogram() +
    labs(
        x = "Hours of Usage per Student",
        y = "Count of Teachers"
    ) +
    theme_minimal()
```

total assignments

```{r}
ggplot(df, aes(total_assign)) +
    geom_histogram() +
    labs(
        x = "Assignments",
        y = "Count of Teachers"
    ) +
    theme_minimal()
```

explore the people with 0 assignments some more... why is this the way it is.

# Ideas

- try a dot and whisker plot to look at variance within schools
